---
title: "bills"
output: html_document
date: "2025-06-11"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

path = "C:/Users/USER/Documents/empirical_evidence_corren"

# Set the working directory for the whole document
# knitr::opts_knit$set(root.dir = path)
knitr::opts_knit$set(root.dir = here::here(path))
```

```{r include=FALSE}
library(ggplot2)
library(dplyr)
library(broom)
library(ggpubr)
library(tidyr)
library(gtable)
library(grid) # for unit.pmax()
library(gridExtra)
library(lubridate)
library(stargazer)
library(vtable)
library(stringr)
library(lmtest)
library(sandwich)
library(purrr)
library("readxl")
library(here)
library(haven)
library(scales)
library(fixest)
library(ggpattern)
library(fst)

```


```{r include=FALSE}
#load(file=paste(here(),"data", "df_withempirical.RData",sep = '/'))

out <- read_fst(paste(here(),"data","out_hearings_enriched.fst",sep = '/'))

df <- out

unique_years <- sort(unique(na.omit(df$year)), decreasing = FALSE)
unique_congress <- sort(unique(na.omit(df$congress)), decreasing = FALSE)

custom_ticks <- unique_years[seq(1, length(unique_years), by = 2)]  # Select every 2nd year
custom_ticks <- seq(1996, 2016, by = 2)


# Define Congress sessions and their corresponding years
congress_mapping <- data.frame(
  congress = unique_congress,
  start_year = seq(1997, by = 2, length.out = 10),
  end_year = seq(1998, by = 2, length.out = 10)
)

# Generate custom ticks for the x-axis
custom_labels <- paste0(custom_ticks, " (", df$congress[match(custom_ticks, df$year)],"th)")



```






# merge data
```{r include=FALSE}
 df_bills <- read.csv(paste(here(),"data", "df_bills.csv",sep = '/'))



df_merged <- df %>%
  filter(bill == 1) %>%
  separate_rows(bill_number, sep = ";") %>%
  mutate(bill_number = str_trim(bill_number)) %>%
  left_join(df_bills, by = "bill_number")


save(df_merged, file=paste(here(),"data", "df_with_bill_sponsors.RData",sep = '/'))
```



```{r include=FALSE}

load(file=paste(here(),"data", "df_with_bill_sponsors.RData",sep = '/'))


tab <- df_merged %>%
  mutate(
    year = as.integer(year),
    congress = as.integer(congress.x)
  ) %>%
  group_by(year, congress.x) %>%
  summarise(
    hearings = n_distinct(packageId),
    speeches = n_distinct(speech),
    .groups = "drop"
  ) %>%
  arrange(year, congress.x) %>%
  filter(hearings > 3) %>%
  filter(!is.na(year), !is.na(congress.x)) %>%   # <-- DROP NA ROWS
  mutate(
    year = as.character(year),
    congress = as.character(congress.x)
  )

totals <- tab %>%
  summarise(
    year = "Total",
    congress = "",
    hearings = sum(hearings),
    speeches = sum(speeches)
  )

tab_final <- bind_rows(tab, totals)

latex_table <- knitr::kable(
  tab_final,
  format = "latex",
  booktabs = TRUE,
  col.names = c("Year", "Congress", "Unique Hearings", "Unique Speech Chunks"),
  caption = "Descriptive statistics by year and Congress."
)


tab_final


```



# Quantile cutoffs
q_low <- quantile(df_merged$bipartisanship_intensity, 0.1, na.rm = TRUE)
q_high <- quantile(df_merged$bipartisanship_intensity, 0.9, na.rm = TRUE)

# Create category
df_merged$bipartisan_category <- with(df_merged, ifelse(
  bipartisanship_intensity <= q_low, "partisan_majority",
  ifelse(bipartisanship_intensity >= q_high, "partisan_minority", "bipartisan")
))



df_merged <- df_merged %>%
  mutate(
    bipartisan_category = case_when(
      is.na(bipartisanship_intensity) ~ NA_character_,
      bipartisanship_intensity <= 0.10 ~ "partisan_majority",
      bipartisanship_intensity >= 0.90 ~ "partisan_minority",
      bipartisanship_intensity > 0.45 & bipartisanship_intensity < 0.55 ~ "bipartisan",
      TRUE ~ "other"
    )
  )


df_merged$bipartisan_category = relevel(factor(df_merged$bipartisan_category), ref = "partisan_minority")
#
# df_merged <- df_merged %>%
#   filter(!is.na(sponsor_party)) %>%
#   filter(sponsor_party %in% c('Democrat','Republican')) %>%
#   mutate(sponsor_party = as.factor(sponsor_party))


```


```{r include=FALSE}
# 
# # Split the strings by ";", trim whitespace, and unlist into a single vector
# bills_list <- unlist(strsplit(df$bill_number, ";"))
# bills_list <- trimws(bills_list)  # Remove leading and trailing whitespace
# 
# # Remove empty strings and NA values, then get unique values
# bills_list <- unique(bills_list[bills_list != "" & !is.na(bills_list)])
# 
# 
# table(df$bill)
# 
# # Step 2: Match the codes to df$var1 and retrieve corresponding var2 values
# matched_var2 <- df_bills$passed[match(bills_list, df_bills$bill_number)]
# 
# # Step 3: Create a list of tuples
# result <- Map(function(code, value) list(code, value), bills_list, matched_var2)
# 
# # Step 4: Convert to a more readable format (optional)
# lookup_table <- lapply(seq_along(bills_list), function(i) c(bills_list[i], matched_var2[i]))

# df_long <- df %>%
#   mutate(bill_number = if_else(bill_number=="",NA,bill_number)) %>%
#   mutate(bill_list = strsplit(bill_number,"; ")) %>%
#   unnest(bill_list)  # Unnest into long format
# 
# # Convert the lookup table to a named vector for efficient matching
# lookup_vector <- setNames(sapply(lookup_table, `[[`, 2), sapply(lookup_table, `[[`, 1))
# 
# # Add the new variable `bill_passed`
# df_long$bill_passed <- ifelse(
#   is.na(df_long$bill_list), 
#   NA,  # Assign NA if `bill` is NA
#   lookup_vector[df_long$bill_list]  # Match the value from the lookup table
# )
# 
# # Handle unmatched bills (set to NA if no match)
# df_long$bill_passed[is.na(df_long$bill_passed) & !is.na(df_long$bill_list)] <- NA

# df_long <- df_long %>%
#   mutate(bill_passed = as.integer(bill_passed))
# 
# df_long <- df_long %>%
#   mutate(empirical_score = mean_score)


# # Plot for HOUSE PASSAGE
# gg_house_pass <- df_merged %>%
#   filter(!is.na(house_pass), !is.na(mean_score)) %>%
#   group_by(house_pass) %>%
#   summarise(
#     mean_score = mean(mean_score, na.rm = TRUE),
#     se = sd(mean_score, na.rm = TRUE) / sqrt(n()),
#     .groups = "drop"
#   ) %>%
#   ggplot(aes(x = factor(house_pass), y = mean_score)) +
#   geom_bar(stat = "identity", fill = "darkgray", width = 0.5) +
#   geom_errorbar(aes(ymin = mean_score - se, ymax = mean_score + se), width = 0.2) +
#   scale_x_discrete(labels = c("0" = "Failed", "1" = "Passed")) +
#   scale_y_continuous(limits = c(0, 0.15)) +
#   labs(x = "House Outcome", y = "Mean Empirical Score") +
#   theme_minimal()
# 
# ggsave(paste(here(), "plots", "house_pass_plot.png", sep = "/"),
#        gg_house_pass, width = 8, height = 6, dpi = 300)
# 
# 
# # Plot for BECOMING LAW
# gg_law_pass <- df_merged %>%
#   filter(!is.na(law_pass), !is.na(mean_score)) %>%
#   group_by(law_pass) %>%
#   summarise(
#     mean_score = mean(mean_score, na.rm = TRUE),
#     se = sd(mean_score, na.rm = TRUE) / sqrt(n()),
#     .groups = "drop"
#   ) %>%
#   ggplot(aes(x = factor(law_pass), y = mean_score)) +
#   geom_bar(stat = "identity", fill = "darkgray", width = 0.5) +
#   geom_errorbar(aes(ymin = mean_score - se, ymax = mean_score + se), width = 0.2) +
#   scale_x_discrete(labels = c("0" = "Failed", "1" = "Passed")) +
#   scale_y_continuous(limits = c(0, 0.15)) +
#   labs(x = "Law Outcome", y = "Mean Empirical Score") +
#   theme_minimal()
# 
# ggsave(paste(here(), "plots", "law_pass_plot.png", sep = "/"),
#        gg_law_pass, width = 8, height = 6, dpi = 300)




summarise_with_ci <- function(data, pass_var, outcome_label_text) {
  data %>%
    filter(!is.na(.data[[pass_var]]), !is.na(mean_score), !is.na(minority)) %>%
    group_by(pass = .data[[pass_var]], minority) %>%
    summarise(
      mean_score = mean(mean_score, na.rm = TRUE),
      n = sum(!is.na(mean_score)),
      sd_score = sd(mean_score, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(
      # Fallback: if n<2 or sd missing, set se=0 so CI = mean
      se = ifelse(is.na(sd_score) | n < 2, 0, sd_score / sqrt(n)),
      # Fallback: if n<2, use z=1.96 (won't matter since se=0)
      tcrit = ifelse(n < 2, 1.96, qt(0.975, df = n - 1)),
      ci_low = mean_score - tcrit * se,
      ci_high = mean_score + tcrit * se,
      outcome_label = outcome_label_text
    ) %>%
    select(-sd_score)
}

house_data <- summarise_with_ci(df_merged, "house_pass", "House Passage")
law_data   <- summarise_with_ci(df_merged, "law_pass",   "Law Passage")

combined_data <- bind_rows(house_data, law_data) %>%
  mutate(
    pass_label = ifelse(pass == 1, "Passed", "Failed"),
    minority_label = ifelse(minority == 1, "Minority Member", "Majority Member"),
    minority_label = factor(minority_label, levels = c("Majority Member", "Minority Member"))
  )

gg_combined <- ggplot(combined_data, aes(x = pass_label, y = mean_score, fill = minority_label)) +
  geom_bar(
    stat = "identity",
    position = position_dodge(width = 0.7),
    width = 0.6
  ) +
  geom_errorbar(
    aes(ymin = ci_low, ymax = ci_high),
    position = position_dodge(width = 0.7),
    width = 0.2
  ) +
  facet_wrap(~ outcome_label) +
  scale_y_continuous(limits = c(0, 0.15)) +
  scale_fill_manual(values = c("Minority Member" = "black", "Majority Member" = "gray50")) +
  labs(
    x = "Outcome",
    y = "Mean Empirical Score",
    title = "Empirical Discourse by Legislative Outcome and Speaker Status",
    fill = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom")


gg_house <- ggplot(
  combined_data %>% filter(outcome_label == "House Passage"),
  aes(x = pass_label, y = mean_score, fill = minority_label)
) +
  geom_bar(
    stat = "identity",
    position = position_dodge(width = 0.7),
    width = 0.6
  ) +
  geom_errorbar(
    aes(ymin = ci_low, ymax = ci_high),
    position = position_dodge(width = 0.7),
    width = 0.2
  ) +
  scale_y_continuous(limits = c(0, 0.15)) +
  scale_fill_manual(
    values = c("Minority Member" = "black", "Majority Member" = "gray50")
  ) +
  labs(
    x = "Outcome",
    y = "Mean Empirical Score",
    title = "Empirical Discourse by House Passage and Speaker Status",
    fill = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom")


gg_law <- ggplot(
  combined_data %>% filter(outcome_label == "Law Passage"),
  aes(x = pass_label, y = mean_score, fill = minority_label)
) +
  geom_bar(
    stat = "identity",
    position = position_dodge(width = 0.7),
    width = 0.6
  ) +
  geom_errorbar(
    aes(ymin = ci_low, ymax = ci_high),
    position = position_dodge(width = 0.7),
    width = 0.2
  ) +
  scale_y_continuous(limits = c(0, 0.15)) +
  scale_fill_manual(
    values = c("Minority Member" = "black", "Majority Member" = "gray50")
  ) +
  labs(
    x = "Outcome",
    y = "Mean Empirical Score",
    title = "Empirical Discourse by Law Passage and Speaker Status",
    fill = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom")


gg_house
# house_data <- df_merged %>%
#   filter(!is.na(house_pass), !is.na(mean_score), !is.na(minority)) %>%
#   group_by(pass = house_pass, minority) %>%
#   summarise(
#     mean_score = mean(mean_score, na.rm = TRUE),
#     se = sd(mean_score, na.rm = TRUE) / sqrt(n()),
#     outcome_label = "House Passage",
#     .groups = "drop"
#   )
# 
# law_data <- df_merged %>%
#   filter(!is.na(law_pass), !is.na(mean_score), !is.na(minority)) %>%
#   group_by(pass = law_pass, minority) %>%
#   summarise(
#     mean_score = mean(mean_score, na.rm = TRUE),
#     se = sd(mean_score, na.rm = TRUE) / sqrt(n()),
#     outcome_label = "Law Passage",
#     .groups = "drop"
#   )
# 
# 
# # Combine
# combined_data <- bind_rows(house_data, law_data) %>%
#   mutate(
#     pass_label = ifelse(pass == 1, "Passed", "Failed"),
#     minority_label = ifelse(minority == 1, "Minority Member", "Majority Member")
#   )
# 
# # Make sure minority_label is a factor with consistent order
# combined_data <- combined_data %>%
#   mutate(
#     minority_label = factor(minority_label, levels = c("Majority Member", "Minority Member"))
#   )
# 
# gg_combined <- ggplot(combined_data, aes(x = pass_label, y = mean_score, fill = minority_label)) +
#   geom_bar(
#     stat = "identity",
#     position = position_dodge(width = 0.7),
#     width = 0.6
#   ) +
#   geom_errorbar(
#     aes(ymin = mean_score - se, ymax = mean_score + se),
#     position = position_dodge(width = 0.7),
#     width = 0.2
#   ) +
#   facet_wrap(~ outcome_label) +
#   scale_y_continuous(limits = c(0, 0.15)) +
#   scale_fill_manual(
#     values = c("Minority Member" = "black", "Majority Member" = "gray50")
#   ) +
#   labs(
#     x = "Outcome",
#     y = "Mean Empirical Score",
#     title = "Empirical Discourse by Legislative Outcome and Speaker Status",
#     fill = NULL
#   ) +
#   theme_minimal(base_size = 13) +
#   theme(legend.position = "bottom")
# 


# Save the combined plot
ggsave(
  filename = paste(here(), "plots", "combined_passage_plot.png", sep = "/"),
  plot = gg_combined,
  width = 10,
  height = 6,
  dpi = 300
)


```


```{r include=FALSE}

summarise_outcome_ci <- function(data, pass_var, outcome_label_text) {
  data %>%
    filter(!is.na(.data[[pass_var]]), !is.na(mean_score)) %>%
    group_by(pass = .data[[pass_var]]) %>%
    summarise(
      mean_score = mean(mean_score, na.rm = TRUE),
      n = sum(!is.na(mean_score)),
      sd_score = sd(mean_score, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(
      se = ifelse(is.na(sd_score) | n < 2, 0, sd_score / sqrt(n)),
      tcrit = ifelse(n < 2, 1.96, qt(0.975, df = n - 1)),
      ci_low = mean_score - tcrit * se,
      ci_high = mean_score + tcrit * se,
      outcome_label = outcome_label_text,
      pass_label = ifelse(pass == 1, "Passed", "Failed")
    ) %>%
    select(-sd_score)
}

house_total <- summarise_outcome_ci(df_merged, "house_pass", "House Passage")
law_total   <- summarise_outcome_ci(df_merged, "law_pass",   "Law Passage")

combined_total <- bind_rows(house_total, law_total)

gg_total <- ggplot(combined_total, aes(x = pass_label, y = mean_score)) +
  geom_col(width = 0.6) +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.2) +
  facet_wrap(~ outcome_label) +
  scale_y_continuous(limits = c(0, 0.15)) +
  labs(
    x = "Outcome",
    y = "Mean Empirical Score",
    title = "Empirical Discourse by Legislative Outcome"
  ) +
  theme_minimal(base_size = 13)
gg_total


ggsave(
  paste(here(), "plots", "outcome_totals_faceted.png", sep = "/"),
  gg_total, width = 7.5, height = 5, dpi = 300
)



gg_house <- ggplot(
  combined_total %>% filter(outcome_label == "House Passage"),
  aes(x = pass_label, y = mean_score)
) +
  geom_col(width = 0.6) +
  geom_errorbar(
    aes(ymin = ci_low, ymax = ci_high),
    width = 0.2
  ) +
  scale_y_continuous(limits = c(0, 0.15)) +
  labs(
    x = "Outcome",
    y = "Mean Empirical Score",
    title = "Empirical Discourse by House Passage"
  ) +
  theme_minimal(base_size = 13)


gg_law <- ggplot(
  combined_total %>% filter(outcome_label == "Law Passage"),
  aes(x = pass_label, y = mean_score)
) +
  geom_col(width = 0.6) +
  geom_errorbar(
    aes(ymin = ci_low, ymax = ci_high),
    width = 0.2
  ) +
  scale_y_continuous(limits = c(0, 0.15)) +
  labs(
    x = "Outcome",
    y = "Mean Empirical Score",
    title = "Empirical Discourse by Law Passage"
  ) +
  theme_minimal(base_size = 13)


ggsave(
  paste(here(), "plots", "house_passage_plot.png", sep = "/"),
  gg_house, width = 7, height = 5, dpi = 300
)


ggsave(
  paste(here(), "plots", "law_passage_plot.png", sep = "/"),
  gg_law, width = 7, height = 5, dpi = 300
)


```



```{r include=FALSE}

gg_bill_passed_time <- df_long %>%
  filter(bill == 1) %>%
  filter(!is.na(bill_passed)) %>%
  filter(!is.na(empirical_score)) %>%
  group_by(years, bill_passed) %>%
  summarise(
    mean_empirical_score = mean(empirical_score, na.rm = TRUE),
    se = sd(empirical_score, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = years, y = mean_empirical_score, color = factor(bill_passed), linetype = factor(bill_passed))) +
  geom_line(size = 1) +  # Lines for each bill outcome
  geom_ribbon(aes(ymin = mean_empirical_score - se, ymax = mean_empirical_score + se, fill = factor(bill_passed)),
              alpha = 0.2, color = NA) +  # Confidence interval shading
  scale_color_manual(
    values = c("0" = "gray", "1" = "black"),
    labels = c("0" = "Failed", "1" = "Passed"),
    name = "Bill Outcome"
  ) +
  scale_linetype_manual(
    values = c("0" = "dashed", "1" = "solid"),
    labels = c("0" = "Failed", "1" = "Passed"),
    name = "Bill Outcome"
  ) +
  scale_fill_manual(
    values = c("0" = "gray", "1" = "black"),
    labels = c("0" = "Failed", "1" = "Passed"),
    name = "Bill Outcome"
  ) +
  labs(
    x = "Year",
    y = "Mean Empirical Score"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12)
  )



ggsave(paste(here(),"plots","bill_passed_time_plot.png",sep = "/"),
  gg_bill_passed_time, width = 8, height = 6, dpi = 300)

```


```{r include=FALSE}


# Start from your grouped summary
df_bills_summary <- df_merged %>%
  filter(bipartisan_category!='other') %>%
  filter(!is.na(minority)) %>%
  group_by(bill_number, minority) %>%
  summarise(
    mean_score = mean(mean_score, na.rm = TRUE),
    n = n(),
    sponsor_party = first(sponsor_party),
    house_pass = first(house_pass),
    law_pass = first(law_pass),
    bipartisan_category = first(bipartisan_category),
    house_maj = first(house_maj),
    divided_house = first(divided_house),
    divided_senate = first(divided_senate),
    years = first(years),
    .groups = "drop"
  )

# Pivot to wide format
df_bills_wide <- df_bills_summary %>%
  pivot_wider(
    names_from = minority,
    values_from = c(mean_score, n),
    names_glue = "{.value}_minority{minority}"
  )

# Compute overall mean_score weighted by n
df_bills_wide <- df_bills_wide %>%
  mutate(
    n_total = coalesce(n_minority0, 0) + coalesce(n_minority1, 0),
    mean_score_overall = (
      coalesce(mean_score_minority0, 0) * coalesce(n_minority0, 0) +
      coalesce(mean_score_minority1, 0) * coalesce(n_minority1, 0)
    ) / n_total
  )
# --- 1. Run models for both outcomes ---

m_house <- lm(
  house_pass ~ mean_score_minority0 + mean_score_minority1 +
    sponsor_party + bipartisan_category +
    house_maj + divided_house + divided_senate + as.factor(years),
  data = df_bills_wide
)

m_house_int <- lm(
  house_pass ~ 
    (mean_score_minority0 + mean_score_minority1) * bipartisan_category +
    sponsor_party +
    house_maj + divided_house + divided_senate + as.factor(years),
  data = df_bills_wide
)

m_law <- lm(
  law_pass ~ mean_score_minority0 + mean_score_minority1 +
    sponsor_party + bipartisan_category +
    house_maj + divided_house + divided_senate + as.factor(years),
  data = df_bills_wide
)

m_law_int <- lm(
  law_pass ~ 
    (mean_score_minority0 + mean_score_minority1) * bipartisan_category +
    sponsor_party +
    house_maj + divided_house + divided_senate + as.factor(years),
  data = df_bills_wide
)

# --- 2. Stargazer Table ---

custom_labels <- c(
  "mean_score_minority0" = "Majority Member Empirical Score",
  "mean_score_minority1" = "Minority Member Empirical Score",

  # Sponsor Party Dummies
  "sponsor_partyRepublican" = "Republican Sponsor",

  # Bipartisan Category Dummies
  "bipartisan_categorybipartisan" = "Bipartisan Sponsors",
  "bipartisan_categorypartisan_majority" = "Majority Sponsors",

  # Interactions
  "mean_score_minority0:bipartisan_categorybipartisan" = "Majority Score × Bipartisan Sponsors",
  "mean_score_minority0:bipartisan_categorypartisan_majority" = "Majority Score × Majority Sponsors",
  "mean_score_minority1:bipartisan_categorybipartisan" = "Minority Score × Bipartisan Sponsors",
  "mean_score_minority1:bipartisan_categorypartisan_majority" = "Minority Score × Majority Sponsors"
)


stargazer(
  m_house, m_house_int,
  m_law, m_law_int,
  type = "latex",
  column.labels = c("House Passage", "", "Signed into Law", ""),
  dep.var.caption = "Dependent Variable:",
  dep.var.labels.include = FALSE,
 covariate.labels = custom_labels,
  omit = c("house_maj", "divided_house","divided_senate","as.factor\\(years\\)"),
  title = "Empirical Discourse and Legislative Passage",
  label = "tab:robust_passage_models",
  out = paste(here(), "plots", "robust_passage_models.latex", sep = "/"),
  align = TRUE,
  no.space = TRUE,
  star.cutoffs = c(0.05, 0.01, 0.001),
  digits = 3,
  add.lines = list(
    c("Interactions", "No", "Yes", "No", "Yes"),
    c("Unified Government Controls", "Yes", "Yes", "Yes", "Yes"),
    c("Year FE", "Yes", "Yes", "Yes", "Yes")
  )
)



summary(m_house_int)

preds <- ggeffects::ggpredict(m_house_int, terms = c("mean_score_minority0", "bipartisan_category"))

marginal_effects_house <- ggplot(preds, aes(x = x, y = predicted, color = group)) +
  geom_line(size = 1.1) +
#  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2, color = NA) +
  labs(
    title = "Marginal Effect of Empirical Score on House Passage",
    x = "Empirical Score",
    y = "Predicted Probability of House Passage",
    color = "Bipartisan Sponsorship",
    fill = "Bipartisan Sponsorship"
  ) +
  theme_minimal()

marginal_effects_house
ggsave(paste(here(), "plots", "marginal_effects_house.png", sep = "/"),
       marginal_effects_house, width = 8, height = 6, dpi = 300)



preds <- ggeffects::ggpredict(m_law_int, terms = c("mean_score", "bipartisan_category"))

marginal_effects_law <- ggplot(preds, aes(x = x, y = predicted, color = group)) +
  geom_line(size = 1.1) +
#  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.2, color = NA) +
  labs(
    title = "Marginal Effect of Empirical Score on Law Passage",
    x = "Empirical Score",
    y = "Predicted Probability of House Passage",
    color = "Bipartisan Sponsorship",
    fill = "Bipartisan Sponsorship"
  ) +
  theme_minimal()


ggsave(paste(here(), "plots", "marginal_effects_law.png", sep = "/"),
       marginal_effects_law, width = 8, height = 6, dpi = 300)



#######
# look at minority status - we need to use the speaker-level data



library(fixest)
library(ggeffects)


m_house_speaker_cluster <- df_merged %>%
  filter(bipartisan_category!="other") %>%
  feols(
  house_pass ~ mean_score * (minority + bipartisan_category) +
    house_maj + divided_house + divided_senate + as.factor(years),
  cluster = ~ bill_number)


preds <- ggpredict(
  m_house_speaker_cluster,
  terms = c("mean_score", "minority", "bipartisan_category")
)

# 1️⃣ Relabel facet names
facet_labels <- c(
  "partisan_majority" = "Majority Sponsors",
  "bipartisan" = "Bipartisan Sponsors",
  "partisan_minority" = "Minority Sponsors"
)

# 2️⃣ Relabel group values
preds$group <- ifelse(preds$group == "1", "Minority Member", "Majority Member")

# 3️⃣ Plot
marginal_effects_house_bystatus <- ggplot(preds, aes(x = x, y = predicted, color = group)) +
  geom_line(size = 1.1) +
  facet_wrap(~ facet, ncol = 3, labeller = as_labeller(facet_labels)) +
  labs(
    title = "Marginal Effect of Empirical Score on House Passage (Clustered SEs)",
    x = "Empirical Score",
    y = "Predicted Effect on House Passage",
    color = NULL  # Remove legend title
  ) +
  theme_minimal(base_size = 14) +  # Set base font size larger
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),  # facet labels
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 14),
    plot.title = element_text(size = 14, face = "bold")
  ) +
    scale_color_manual(
    values = c("Minority Member" = "black", "Majority Member" = "gray")  # or choose your preferred colors
  )


ggsave(paste(here(), "plots", "marginal_effects_house_bystatus.png", sep = "/"),
       marginal_effects_house_bystatus, width = 8, height = 6, dpi = 300)





# Filter preds for Majority Sponsors
preds_majority_sponsors <- preds %>%
  dplyr::filter(facet == "partisan_majority")

# Plot without facets
marginal_effects_house_majority <- ggplot(preds_majority_sponsors, aes(x = x, y = predicted, color = group)) +
  geom_line(size = 1.1) +
  labs(
    title = "Marginal Effect of Empirical Score on House Passage\n(Majority Sponsors, Clustered SEs)",
    x = "Empirical Score",
    y = "Predicted Effect on House Passage",
    color = NULL
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 16),  # facet labels
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 14),
    plot.title = element_text(size = 14, face = "bold")
  ) +
  scale_color_manual(
    values = c("Minority Member" = "black", "Majority Member" = "gray50")
  )


marginal_effects_house_majority


```

```{r include=FALSE}
# 
# gg_bipartisanship_intensity <- df_merged %>%
#   sample_frac(0.01) %>%
#   filter(!is.na(bipartisanship_intensity), !is.na(mean_score)) %>%
#   ggplot(aes(x = bipartisanship_intensity, y = mean_score)) +
#   geom_point(alpha = 0.3, color = "steelblue") +
#   geom_smooth(method = "loess", se = TRUE, color = "darkred") +
#   labs(
#     x = "Bipartisanship Intensity (Minority Share of Sponsors)",
#     y = "Mean Empirical Score",
#     title = "Relationship Between Bipartisanship and Empirical Speech"
#   ) +
#   theme_minimal()
# 
# 
# ggsave(paste(here(), "plots", "bipartisanship_intensity_plot.png", sep = "/"),
#        gg_bipartisanship_intensity, width = 8, height = 6, dpi = 300)
# 
# 
# gg_extremism_score <- df_merged %>%
#     sample_frac(0.01) %>%
#   filter(!is.na(extremism_score), !is.na(mean_score)) %>%
#   ggplot(aes(x = extremism_score, y = mean_score)) +
#   geom_point(alpha = 0.3, color = "steelblue") +
#   geom_smooth(method = "loess", se = TRUE, color = "darkred") +
#   labs(
#     x = "Extremism_score Intensity)",
#     y = "Mean Empirical Score",
#     title = "Relationship Between extremism_score and Empirical Speech"
#   ) +
#   theme_minimal()
# 
# 
# ggsave(paste(here(), "plots", "extremism_score_plot.png", sep = "/"),
#        gg_extremism_score, width = 8, height = 6, dpi = 300)
# 
# 
# 
# 
# df_merged %>%
#   sample_frac(0.01) %>%
#   group_by(sponsor_majority,bipartisan) %>%
#   summarise(empirical = mean(mean_score,na.rm=TRUE))


# # Calculate mean and standard deviation
# mu <- mean(df_merged$bipartisanship_intensity, na.rm = TRUE)
# sigma <- sd(df_merged$bipartisanship_intensity, na.rm = TRUE)
# 
# # Categorize using SD-based thresholds
# df_merged$bipartisan_category <- with(df_merged, ifelse(
#   bipartisanship_intensity < (mu - sigma), "partisan_majority",
#   ifelse(bipartisanship_intensity > (mu + sigma), "partisan_minority", "bipartisan")
# ))

```

```{r include=FALSE}

# Aggregate to bill level first for all plots
df_bill_level <- df_merged %>%
  filter(!is.na(bipartisan_category), !is.na(sponsor_party)) %>%
  filter(sponsor_party %in% c("Democrat", "Republican")) %>%
  group_by(bill_number, bipartisan_category, sponsor_party, years) %>%
  summarise(mean_score = mean(mean_score, na.rm = TRUE), .groups = "drop")

# Plot 1: Total by bipartisan_category (no party breakdown)
g_bipartisan_category_total <- df_bill_level %>%
  group_by(bipartisan_category) %>%
  summarise(mean_score = mean(mean_score), se = sd(mean_score)/sqrt(n()), .groups = "drop") %>%
  ggplot(aes(x = bipartisan_category, y = mean_score)) +
  geom_col(fill = "steelblue", width = 0.6) +
  geom_errorbar(aes(ymin = mean_score - se, ymax = mean_score + se), width = 0.2) +
  labs(
    title = "Average Empirical Score by Bipartisan Category",
    x = "Bipartisan Category",
    y = "Mean Empirical Score"
  ) +
  theme_minimal()

ggsave(paste(here(), "plots", "bipartisan_category_total_plot.png", sep = "/"),
       g_bipartisan_category_total, width = 8, height = 6, dpi = 300)

# Plot 2: By bipartisan_category and sponsor_party
g_bipartisan_category <- df_bill_level %>%
  group_by(bipartisan_category, sponsor_party) %>%
  summarise(mean_score = mean(mean_score), se = sd(mean_score)/sqrt(n()), .groups = "drop") %>%
  ggplot(aes(x = bipartisan_category, y = mean_score, fill = sponsor_party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_errorbar(aes(ymin = mean_score - se, ymax = mean_score + se),
                position = position_dodge(width = 0.7), width = 0.2) +
  labs(
    title = "Average Empirical Score by Bipartisan Category and Sponsor Party",
    x = "Bipartisan Category",
    y = "Mean Empirical Score",
    fill = "Sponsor Party"
  ) +
  theme_minimal() +
  scale_fill_manual(values = c("Democrat" = "blue", "Republican" = "red"))

ggsave(paste(here(), "plots", "bipartisan_category_plot.png", sep = "/"),
       g_bipartisan_category, width = 8, height = 6, dpi = 300)

# Plot 3: Over time by bipartisan_category and sponsor_party
g_bipartisan_sponsor_overtime <- df_bill_level %>%
  group_by(years, bipartisan_category, sponsor_party) %>%
  summarise(mean_score = mean(mean_score), .groups = "drop") %>%
  ggplot(aes(x = years, y = mean_score, color = sponsor_party, linetype = bipartisan_category)) +
  geom_line(linewidth = 1.1) +
  geom_point() +
  labs(
    title = "Empirical Score Over Time by Category and Sponsor Party",
    x = "Year",
    y = "Mean Empirical Score",
    color = "Sponsor Party",
    linetype = "Bipartisan Category"
  ) +
  theme_minimal() +
  scale_color_manual(values = c("Democrat" = "blue", "Republican" = "red"))

ggsave(paste(here(), "plots", "bipartisan_category_overtime.png", sep = "/"),
       g_bipartisan_sponsor_overtime, width = 8, height = 6, dpi = 300)

# Plot 4: Over time by bipartisan_category only
g_bipartisan_sponsor_overtime_total <- df_bill_level %>%
  group_by(years, bipartisan_category) %>%
  summarise(mean_score = mean(mean_score), .groups = "drop") %>%
  ggplot(aes(x = years, y = mean_score, linetype = bipartisan_category)) +
  geom_line(linewidth = 1.1) +
  geom_point() +
  labs(
    title = "Empirical Score Over Time by Bipartisan Category",
    x = "Year",
    y = "Mean Empirical Score",
    linetype = "Bipartisan Category"
  ) +
  theme_minimal()

ggsave(paste(here(), "plots", "bipartisan_category_overtime_total.png", sep = "/"),
       g_bipartisan_sponsor_overtime_total, width = 8, height = 6, dpi = 300)


```

```{r include=FALSE}

summarise_cell_ci <- function(data, pass_var) {
  data %>%
    filter(
      !is.na(bipartisan_category),
      bipartisan_category != "other",
      !is.na(minority),
      !is.na(.data[[pass_var]]),
      !is.na(mean_score)
    ) %>%
    group_by(bipartisan_category, minority, pass = .data[[pass_var]]) %>%
    summarise(
      mean_score = mean(mean_score, na.rm = TRUE),
      n = sum(!is.na(mean_score)),
      sd_score = sd(mean_score, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(
      # Fallback: n<2 or sd missing => CI collapses to mean
      se = ifelse(is.na(sd_score) | n < 2, 0, sd_score / sqrt(n)),
      tcrit = ifelse(n < 2, 1.96, qt(0.975, df = n - 1)),
      ci_low = mean_score - tcrit * se,
      ci_high = mean_score + tcrit * se
    ) %>%
    select(-sd_score)
}

# X-axis labels for bipartisan categories
bipartisan_labels <- c(
  partisan_minority = "Minority Sponsors",
  bipartisan = "Bipartisan Sponsors",
  partisan_majority = "Majority Sponsors"
)


g1_data <- summarise_cell_ci(df_merged, "house_pass") %>%
  mutate(
    minority_label = ifelse(minority == 1, "Minority", "Majority"),
    house_pass_label = ifelse(pass == 1, "Passed", "Failed")
  )

g1 <- ggplot(
  g1_data,
  aes(
    x = bipartisan_category,
    y = mean_score,
    fill = house_pass_label,
    pattern = minority_label
  )
) +
  geom_bar_pattern(
    stat = "identity",
    position = position_dodge(width = 0.8),
    width = 0.7,
    pattern_fill = "black",
    pattern_angle = 45,
    pattern_density = 0.2,
    pattern_spacing = 0.05,
    color = "black",
    pattern_key_scale_factor = 0.6
  ) +
  geom_errorbar(
    aes(ymin = ci_low, ymax = ci_high),
    position = position_dodge(width = 0.8),
    width = 0.2,
    color = "black"
  ) +
  scale_x_discrete(labels = bipartisan_labels) +
  scale_fill_manual(
    values = c("Passed" = "darkgreen", "Failed" = "firebrick"),
    name = "Bill Passage"
  ) +
  scale_pattern_manual(
    values = c("Majority" = "none", "Minority" = "stripe"),
    name = "Speaker Status"
  ) +
  guides(
    fill = guide_legend(override.aes = list(pattern = "none"), order = 1),
    pattern = guide_legend(override.aes = list(fill = "grey"), order = 2)
  ) +
  labs(
    title = "Empirical Score by Bipartisan Category and Bill Passage (House)",
    x = NULL,
    y = "Mean Empirical Score"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

ggsave(
  paste(here(), "plots", "bipartisan_category_bill_pass_house.png", sep = "/"),
  g1, width = 8, height = 6, dpi = 300
)

g1


g2_data <- summarise_cell_ci(df_merged, "law_pass") %>%
  mutate(
    minority_label = ifelse(minority == 1, "Minority", "Majority"),
    law_pass_label = ifelse(pass == 1, "Passed", "Failed")
  )

g2 <- ggplot(
  g2_data,
  aes(
    x = bipartisan_category,
    y = mean_score,
    fill = law_pass_label,
    pattern = minority_label
  )
) +
  geom_bar_pattern(
    stat = "identity",
    position = position_dodge(width = 0.8),
    width = 0.7,
    pattern_fill = "black",
    pattern_angle = 45,
    pattern_density = 0.2,
    pattern_spacing = 0.05,
    color = "black",
    pattern_key_scale_factor = 0.6
  ) +
  geom_errorbar(
    aes(ymin = ci_low, ymax = ci_high),
    position = position_dodge(width = 0.8),
    width = 0.2,
    color = "black"
  ) +
  scale_x_discrete(labels = bipartisan_labels) +
  scale_fill_manual(
    values = c("Passed" = "darkgreen", "Failed" = "firebrick"),
    name = "Bill Passage"
  ) +
  scale_pattern_manual(
    values = c("Majority" = "none", "Minority" = "stripe"),
    name = "Speaker Status"
  ) +
  guides(
    fill = guide_legend(override.aes = list(pattern = "none"), order = 1),
    pattern = guide_legend(override.aes = list(fill = "grey"), order = 2)
  ) +
  labs(
    title = "Empirical Score by Bipartisan Category and Bill Passage (Signed into Law)",
    x = NULL,
    y = "Mean Empirical Score"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

ggsave(
  paste(here(), "plots", "bipartisan_category_bill_pass_law.png", sep = "/"),
  g2, width = 8, height = 6, dpi = 300
)



# # Define x-axis labels
# bipartisan_labels <- c(
#   "partisan_minority" = "Minority Sponsors",
#   "bipartisan" = "Bipartisan Sponsors",
#   "partisan_majority" = "Majority Sponsors"
# )
# 
# # HOUSE PASSAGE
# # House passage data
# g1_data <- df_merged %>%
#   filter(
#     !is.na(bipartisan_category),
#     bipartisan_category != "other",
#     !is.na(minority),
#     !is.na(house_pass)
#   ) %>%
#   group_by(bipartisan_category, minority, house_pass) %>%
#   summarise(
#     mean_score = mean(mean_score, na.rm = TRUE),
#     se = sd(mean_score, na.rm = TRUE) / sqrt(n()),
#     .groups = "drop"
#   ) %>%
#   mutate(
#     minority_label = ifelse(minority == 1, "Minority", "Majority"),
#     house_pass_label = ifelse(house_pass == 1, "Passed", "Failed")
#   )
# 
# g1 <- ggplot(
#   g1_data,
#   aes(
#     x = bipartisan_category,
#     y = mean_score,
#     fill = house_pass_label,
#     pattern = minority_label
#   )
# ) +
#   geom_bar_pattern(
#     stat = "identity",
#     position = position_dodge(width = 0.8),
#     width = 0.7,
#     pattern_fill = "black",
#     pattern_angle = 45,
#     pattern_density = 0.2,
#     pattern_spacing = 0.05,
#     color = "black",
#     pattern_key_scale_factor = 0.6
#   ) +
#   geom_errorbar(
#     aes(ymin = mean_score - se, ymax = mean_score + se),
#     position = position_dodge(width = 0.8),
#     width = 0.2,
#     color = "black"
#   ) +
#   scale_x_discrete(labels = bipartisan_labels) +
#   scale_fill_manual(
#     values = c("Passed" = "darkgreen", "Failed" = "firebrick"),
#     name = "Bill Passage"
#   ) +
#   scale_pattern_manual(
#     values = c("Majority" = "none", "Minority" = "stripe"),
#     name = "Speaker Status"
#   ) +
#   guides(
#     fill = guide_legend(
#       override.aes = list(pattern = "none"),
#       order = 1
#     ),
#     pattern = guide_legend(
#       override.aes = list(fill = "grey"),
#       order = 2
#     )
#   ) +
#   labs(
#     title = "Empirical Score by Bipartisan Category and Bill Passage (House)",
#     x = NULL,
#     y = "Mean Empirical Score"
#   ) +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 30, hjust = 1))
# 
# ggsave(paste(here(), "plots", "bipartisan_category_bill_pass_house.png", sep = "/"),
#        g1, width = 8, height = 6, dpi = 300)
# 
# 
# 
# # LAW PASSAGE
# # Law passage data
# g2_data <- df_merged %>%
#   filter(
#     !is.na(bipartisan_category),
#     bipartisan_category != "other",
#     !is.na(minority),
#     !is.na(law_pass)
#   ) %>%
#   group_by(bipartisan_category, minority, law_pass) %>%
#   summarise(
#     mean_score = mean(mean_score, na.rm = TRUE),
#     se = sd(mean_score, na.rm = TRUE) / sqrt(n()),
#     .groups = "drop"
#   ) %>%
#   mutate(
#     minority_label = ifelse(minority == 1, "Minority", "Majority"),
#     law_pass_label = ifelse(law_pass == 1, "Passed", "Failed")
#   )
# 
# g2 <- ggplot(
#   g2_data,
#   aes(
#     x = bipartisan_category,
#     y = mean_score,
#     fill = law_pass_label,
#     pattern = minority_label
#   )
# ) +
#   geom_bar_pattern(
#     stat = "identity",
#     position = position_dodge(width = 0.8),
#     width = 0.7,
#     pattern_fill = "black",
#     pattern_angle = 45,
#     pattern_density = 0.2,
#     pattern_spacing = 0.05,
#     color = "black",
#     pattern_key_scale_factor = 0.6
#   ) +
#   geom_errorbar(
#     aes(ymin = mean_score - se, ymax = mean_score + se),
#     position = position_dodge(width = 0.8),
#     width = 0.2,
#     color = "black"
#   ) +
#   scale_x_discrete(labels = bipartisan_labels) +
#   scale_fill_manual(
#     values = c("Passed" = "darkgreen", "Failed" = "firebrick"),
#     name = "Bill Passage"
#   ) +
#   scale_pattern_manual(
#     values = c("Majority" = "none", "Minority" = "stripe"),
#     name = "Speaker Status"
#   ) +
#   guides(
#     fill = guide_legend(
#       override.aes = list(pattern = "none"),
#       order = 1
#     ),
#     pattern = guide_legend(
#       override.aes = list(fill = "grey"),
#       order = 2
#     )
#   ) +
#   labs(
#     title = "Empirical Score by Bipartisan Category and Bill Passage (Signed into Law)",
#     x = NULL,
#     y = "Mean Empirical Score"
#   ) +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 30, hjust = 1))
# 
# ggsave(paste(here(), "plots", "bipartisan_category_bill_pass_law.png", sep = "/"),
#        g2, width = 8, height = 6, dpi = 300)


# library(ggpattern)
# 
# 
# g1 <- df_merged %>%
#   filter(
#     !is.na(bipartisan_category),
#     !is.na(minority),
#     !is.na(house_pass)
#   ) %>%
#   group_by(bipartisan_category, minority, house_pass) %>%
#   summarise(mean_score = mean(mean_score, na.rm = TRUE), .groups = "drop") %>%
#   mutate(
#     minority_label = ifelse(minority == 1, "Minority", "Majority"),
#     house_pass_label = ifelse(house_pass == 1, "Passed", "Failed"),
#     group = interaction(minority_label, house_pass_label, sep = " / ")
#   ) %>% 
# ggplot(aes(
#     x = bipartisan_category,
#     y = mean_score,
#     fill = house_pass_label,
#     pattern = minority_label
#   )
# ) +
#   geom_bar_pattern(
#     stat = "identity",
#     position = position_dodge(width = 0.8),
#     width = 0.7,
#     pattern_fill = "black",           # pattern color
#     pattern_angle = 45,
#     pattern_density = 0.2,
#     pattern_spacing = 0.05,
#     color = "black",                  # bar outline
#     pattern_key_scale_factor = 0.6
#   ) +
#   scale_fill_manual(
#     values = c("Passed" = "darkgreen", "Failed" = "firebrick")
#   ) +
#   scale_pattern_manual(
#     values = c("Majority" = "none", "Minority" = "stripe")
#   ) +
#   labs(
#     title = "Empirical Score by Bipartisan Category and Bill Passage (House)",
#     x = "Bipartisan Category",
#     y = "Mean Empirical Score",
#     fill = "Bill Passage",
#     pattern = "Speaker Status"
#   ) +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 30, hjust = 1))
# 
# 
# ggsave(paste(here(), "plots", "bipartisan_category_bill_pass_house.png", sep = "/"),
#        g1, width = 8, height = 6, dpi = 300)
# 
# 
# g2 <- df_merged %>%
#   filter(
#     !is.na(bipartisan_category),
#     !is.na(minority),
#     !is.na(law_pass)
#   ) %>%
#   group_by(bipartisan_category, minority, law_pass) %>%
#   summarise(mean_score = mean(mean_score, na.rm = TRUE), .groups = "drop") %>%
#   mutate(
#     minority_label = ifelse(minority == 1, "Minority", "Majority"),
#     law_pass_label = ifelse(law_pass == 1, "Passed", "Failed"),
#     group = interaction(minority_label, law_pass, sep = " / ")
#   ) %>% 
# ggplot(aes(
#     x = bipartisan_category,
#     y = mean_score,
#     fill = law_pass_label,
#     pattern = minority_label
#   )
# ) +
#   geom_bar_pattern(
#     stat = "identity",
#     position = position_dodge(width = 0.8),
#     width = 0.7,
#     pattern_fill = "black",           # pattern color
#     pattern_angle = 45,
#     pattern_density = 0.2,
#     pattern_spacing = 0.05,
#     color = "black",                  # bar outline
#     pattern_key_scale_factor = 0.6
#   ) +
#   scale_fill_manual(
#     values = c("Passed" = "darkgreen", "Failed" = "firebrick")
#   ) +
#   scale_pattern_manual(
#     values = c("Majority" = "none", "Minority" = "stripe")
#   ) +
#   labs(
#     title = "Empirical Score by Bipartisan Category and Bill Passage (Signed into Law)",
#     x = "Bipartisan Category",
#     y = "Mean Empirical Score",
#     fill = "Bill Passage",
#     pattern = "Speaker Status"
#   ) +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 30, hjust = 1))
# 
# 
# ggsave(paste(here(), "plots", "bipartisan_category_bill_pass_law.png", sep = "/"),
#        g2, width = 8, height = 6, dpi = 300)

```



```{r include=FALSE}
df_bills <- read.csv(paste(here(),"data", "df_bills.csv",sep = '/'))


# Plot the distribution

g_intensity_dist <- ggplot(df_bills, aes(x = bipartisanship_intensity)) +
  geom_histogram(binwidth = 0.05, fill = "steelblue", color = "white", boundary = 0) +
  labs(
    x = "Bipartisanship Score",
    y = "Count"
  ) +
  theme_minimal()


ggsave(paste(here(), "plots", "bipartisan_intensity_dist.png", sep = "/"),
       g_intensity_dist,
       width = 8,
       height = 6,
       dpi = 300)



# df_bills <- df_bills %>%
#   mutate(
#     bipartisan_category = case_when(
#       is.na(bipartisanship_intensity) ~ NA_character_,
#       bipartisanship_intensity <= 0.10 ~ "partisan_majority",
#       bipartisanship_intensity >= 0.90 ~ "partisan_minority",
#       TRUE ~ "bipartisan"
#     )
#   )
# 
# 
# 
# g_cat_dist_1 <- df_bills %>%
#   mutate(bipartisan_category = factor(
#     bipartisan_category,
#     levels = c("partisan_majority", "bipartisan", "partisan_minority")
#   )) %>%
#   ggplot(aes(x = bipartisan_category)) +
#   geom_bar(fill = "steelblue") +
#   labs(
#     title = "Distribution: Majority (0-0.1), Bipartisan (0.1-0.9), Minority (0.9-1)",
#     x = "Bipartisan Category",
#     y = "Count"
#   ) +   scale_x_discrete(labels = c(
#   "partisan_majority" = "Majority",
#   "bipartisan" = "Bipartisan",
#   "partisan_minority" = "Minority"
# )) +
#   theme_minimal()

df_bills <- df_bills %>%
  mutate(
    bipartisan_category = case_when(
      is.na(bipartisanship_intensity) ~ NA_character_,
      bipartisanship_intensity <= 0.10 ~ "partisan_majority",
      bipartisanship_intensity >= 0.90 ~ "partisan_minority",
      bipartisanship_intensity > 0.45 & bipartisanship_intensity < 0.55 ~ "bipartisan",
      TRUE ~ "other"
    )
  )


df_summary <- df_bills %>%
  filter(!is.na(bipartisan_category), bipartisan_category != "other") %>%
  group_by(bipartisan_category) %>%
  summarise(
    n = n(),
    pass_rate = mean(house_pass, na.rm = TRUE)
  ) %>%
  mutate(bipartisan_category = factor(
    bipartisan_category,
    levels = c("partisan_majority", "bipartisan", "partisan_minority")
  ))

g_cat_dist <- ggplot(df_summary, aes(x = bipartisan_category, y = n)) +
  geom_col(fill = "darkorange", alpha = 0.7) +
  geom_col(aes(y = n * pass_rate), fill = "black", alpha = 0.4) +
  labs(
    # title = "Distribution: Majority (0-0.1), Bipartisan (0.45-0.55), Minority (0.9-1)",
    x = "Bipartisan Category",
    y = "Count"
  ) +   scale_x_discrete(labels = c(
  "partisan_majority" = "Majority",
  "bipartisan" = "Bipartisan",
  "partisan_minority" = "Minority"
)) +
  theme_minimal()




# df_bills <- df_bills %>%
#   mutate(
#     bipartisan_category_3 = case_when(
#       is.na(bipartisanship_intensity) ~ NA_character_,
#       bipartisanship_intensity <= 0.20 ~ "partisan_majority",
#       bipartisanship_intensity >= 0.80 ~ "partisan_minority",
#       bipartisanship_intensity > 0.4 & bipartisanship_intensity < 0.6 ~ "bipartisan",
#       TRUE ~ "other"
#     )
#   )
# 
# g_cat_dist_3 <- df_bills %>%
#   mutate(bipartisan_category_3 = factor(
#     bipartisan_category_3,
#     levels = c("partisan_majority", "bipartisan", "partisan_minority")
#   )) %>%  filter(bipartisan_category_3 != "other") %>%  # Optionally exclude 'other'
#   ggplot(aes(x = bipartisan_category_3)) +
#   geom_bar(fill = "seagreen") +
#   labs(
#     title = "Distribution: Majority (0-0.2), Bipartisan (0.4-0.6), Minority (0.8-1)",
#     x = "Bipartisan Category",
#     y = "Count"
#   ) +
#   scale_x_discrete(labels = c(
#   "partisan_majority" = "Majority",
#   "bipartisan" = "Bipartisan",
#   "partisan_minority" = "Minority"
# )) +
#   theme_minimal()






# ggsave(paste(here(), "plots", "bipartisan_cat_dist_01_09.png", sep = "/"),
#        g_cat_dist_1,
#        width = 8,
#        height = 6,
#        dpi = 300)


ggsave(paste(here(), "plots", "bipartisan_cat_dist_45_55.png", sep = "/"),
       g_cat_dist,
       width = 8,
       height = 6,
       dpi = 300)


# ggsave(paste(here(), "plots", "bipartisan_cat_dist_4_6.png", sep = "/"),
#        g_cat_dist_3,
#        width = 8,
#        height = 6,
#        dpi = 300)



```

